\textbf{Computational Fuzzy Extractors}

### 2013-05-14 trunk/CompFuzzExt.tex
Notes for sections 4 and 5

\documentclass[11pt]{article}
\def\shownotes{0}

@@

\begin{abstract} 
%\lnote{This is an old abstract, no longer correct}
Fuzzy extractors derive cryptographically strong keys from noisy sources.  They are traditionally built by combining a secure sketch and a randomness extractor.  Secure sketches remove noise from correct errors in the source while revealing little about the source.  Randomness extractors convert high entropy sources to the uniform distribution.  %Secure sketches necessarily reveal some information about the noisy secret, and thus the derived key in fuzzy extractors has lower entropy than the source.  The minimal entropy loss 
%One-message information reconciliation protocols called secure sketches remove noise
%from secrets without revealing too much about them.  They are a crucial ingredient in
%fuzzy extractors, which provide an information-theoretic mechanism for reliable key derivation from noisy sources.

@@

Authentication generally require a secret drawn from some high-entropy source.  One of the primary building blocks for authentication is reliable key derivation.  Unfortunately, many sources that contain sufficient entropy to derive a key are  noisy, and provide similar, but not identical secret values at each reading (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).  %Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.

@@

%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $n - \log |B_t(\cdot)|$.  Since random linear codes already achieve min-entropy $n(1-o(1)) - \log B_t(\cdot)$ on uniform inputs, it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.

@@

\begin{definition}
\label{def:relaxed hill}
Let $(W, X)$ be a pair of random variables.  $W$ has 
\emph{relaxed HILL entropy} at least $k$ conditioned on $X$,
denoted $H^{\hillrlx}_{\epsilon, s_{sec}}(W|X)\geq k$ if there exists a joint distribution $(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, X),(Y,Z))\leq \epsilon$.
\end{definition}

@@

The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.  In order to have  $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y, Z$ such that $\Hav(Y | Z)\geq \tilde{m}$ and $(Y, Z)$ is computationally indistinguishable from $(W, \sketch(W))$.  Sample a sketch $s\leftarrow \sketch(W)$. We know that $\sketch$ followed by $\rec$ likely succeeds on $W|s$  (i.e., $\rec (w', s) = w$ with high probability for $w\leftarrow W|s$ and $w'\leftarrow B_t(w)$).  %So, by indistinguishability, it must also succeed on $Y$. 
 Consider the following experiment: 1) sample $z\leftarrow Z$, 2) draw $y\leftarrow Y|z$ and 3) $y'\leftarrow B_t(y)$. By indistinguishability $\rec (y',z) = y$ with high probability.
 This means we can construct a large set $C$ from the support of $Y|z$.  $C$ will be an error correcting code and $\rec$ an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.

To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
\begin{definition}
\label{def:neighborhood samplable}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{neigh}, t)$-\emph{neighborhood samplable} if there exists a randomized circuit $\neigh$ of size $s_{neigh}$ that for all $t'\leq t$, $\neigh (x, t')$ outputs a random point at distance $t'$ of $x$.  
%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
%\[
%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
%\]
\end{definition}
%We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.  While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context. \lnote{ do we need this? if distance is exactly $t'$, then the point is different as long as $t'>0$.  So why not just say "exactly $t'$ in the definition?}

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
\label{def:shannon-code}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]<\epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compare to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

@@

 \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]<\epsilon$.
\end{definition}
An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.  See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.  An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.  We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.  There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We can now formalize the intuition above and show that a sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Let $s_{rec}$ denote the size of the circuit that computes $\rec$.  If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

%It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
For the Hamming metric, any Shannon code (as defined in Definition~\ref{def:shannon-code}) can be converted into an information-theoretic secure sketch~(as described in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).  The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the bits of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}\geq t(s_{rec} + n\log |Z|)$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+t\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

@@

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
For a distribution $(X, Z)$, we say that $X$ has \emph{unpredictability entropy} at least $k$ conditioned on $Z,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (X|Z) \geq k$, if there exists a collection of distributions $Y_z$ (giving rise to a joint distribution $(Y, Z)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((X, Z),(Y, Z))\leq \epsilon$, and for all circuits $C$ of size $s_{sec}$,
\[
\Pr[C(Z) = Y ] \leq 2^{-k}
.\]
\end{definition}
We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch} with the security requirement replaced with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{lem:unp extraction} 
Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
\end{lemma}
Thus, if a sketch retained unpredictability entropy we could build a computational fuzzy extractor~(using the construction in \lemref{lem:fuzzy ext construction}).  
Unfortunately, the unpredictability entropy conditioned on the sketch must decrease as $t$ increases.  
%An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.  %That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.  
The formal statement is below:
\begin{theorem}
\label{thm:imp of unp entropy}
Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be an unpredictability-entropy \\$(Z^n, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
\end{theorem}
This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.  This means we cannot construct a good code out of the points of $Y$.  In \secref{sec:proof of imp unp entropy}, we prove a stronger theorem for larger class of metric spaces and for a relaxed notion of unpredictability entropy.%Our bound is a result of the Hamming bound for the space.

>>>>

\documentclass[11pt]{article}
\def\shownotes{1}

@@

\begin{abstract} 
%\lnote{This is an old abstract, no longer correct}
Fuzzy extractors derive cryptographically strong keys from noisy sources.  They are traditionally built by combining a secure sketch and a randomness extractor.  Secure sketches remove noise from the source while revealing little information about the source.  Randomness extractors convert high entropy sources to the uniform distribution.  %Secure sketches necessarily reveal some information about the noisy secret, and thus the derived key in fuzzy extractors has lower entropy than the source.  The minimal entropy loss 
%One-message information reconciliation protocols called secure sketches remove noise
%from secrets without revealing too much about them.  They are a crucial ingredient in
%fuzzy extractors, which provide an information-theoretic mechanism for reliable key derivation from noisy sources.

@@

Authentication generally requires a secret drawn from some high-entropy source.  One of the primary building blocks for authentication is reliable key derivation.  Unfortunately, many sources that contain sufficient entropy to derive a key are  noisy, and provide similar, but not identical secret values at each reading (examples of such sources include biometrics~\cite{daugman2004}, human memory~\cite{zviran1993comparison}, pictorial passwords~\cite{brostoff2000passfaces}, measurements of capacitance~\cite{tuyls2006puf}, timing~\cite{suh2007physical}, motion~\cite{castelluccia2005shake},  quantum information~\cite{bennett1988privacy} etc.).  %Information reconciliation protocols~\cite{bennett1988privacy} remove the noise without revealing the secrets.

@@

%We will not provide formal definitions for these sketches but use the notation HILL/unpredictability~$(\mathcal{M}, m, \tilde{m}, t)$-secure sketch to denote a sketch that retains $\tilde{m}$ bits of HILL~(resp. unpredictability) entropy when given a source with $m$ bits of entropy.  
In \secref{sec:imp HILL sketch} we show that a sketch that retains HILL entropy implies a sketch that retains nearly the same amount of min-entropy.  In \secref{sec:imp unp sketch}, we show that the computational unpredictability of a sketch is at most $\log |\mathcal{M}| - \log |B_t(\cdot)|$.  Random linear codes~(in the Hamming metric) already achieve min-entropy $\log |\mathcal{M}|(1-o(1)) - \log B_t(\cdot)$ on uniform inputs, so it seems that relaxing security of sketches from information-theoretic to computational does not help---at least not on uniform inputs.\bnote{I changed this bound to be size of metric space before it was just n which was wrong.  Do we prefer $n\log Z$?}  In \secref{ssec:avoiding bounds}, we discuss mechanisms for avoiding these bounds.

@@

\begin{definition}
\label{def:relaxed hill}
Let $(W, S)$ be a pair of random variables.  $W$ has 
\emph{relaxed HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hillrlx}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon$.
\end{definition}

@@

The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.  In order to have  $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $X, Y$ such that $\Hav(X | Y)\geq \tilde{m}$ and $(X, Y)$ is computationally indistinguishable from $(W, \sketch(W))$.  Sample a sketch $s\leftarrow \sketch(W)$. We know that $\sketch$ followed by $\rec$ likely succeeds on $W|s$  (i.e., $\rec (w', s) = w$ with high probability for $w\leftarrow W|s$ and $w'\leftarrow B_t(w)$).  %So, by indistinguishability, it must also succeed on $Y$. 
 Consider the following experiment: 1) sample $y\leftarrow Y$, 2) draw $x\leftarrow X|y$ and 3) $x'\leftarrow B_t(x)$. By indistinguishability $\rec (x',z) = x$ with high probability.
 This means we can construct a large set $\mathcal{C}$ from the support of $X|y$.  $\mathcal{C}$ will be an error correcting code and $\rec$ an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.

To make this intuition precise, we need an additional technical condition:  sampling a random neighbor of a point is efficient.
\begin{definition}
\label{def:neighborhood samplable}
We say a metric space $(\mathcal{M}, \dis)$ is $(s_{neigh}, t)$-\emph{neighborhood samplable} if there exists a randomized circuit $\neigh$ of size $s_{neigh}$ that for all $t'\leq t$, $\neigh (w, t')$ outputs a random point at distance $t'$ of $w$.  
%That is $\exists \sample$ of size at most $s$ such that $\forall x\in \mathcal{M},$
%\[
%\Delta(\sample(x, t') , \{x'| \dis(x,x') = t'\})=0
%\]
\end{definition}
%We require that \sample returns a point different from $x$ to ensure that each $B_t(x)$ contains at least one other point.  While we could consider metric spaces where balls only contain their center, secure sketches are not interesting in this context. \lnote{ do we need this? if distance is exactly $t'$, then the point is different as long as $t'>0$.  So why not just say "exactly $t'$ in the definition?}

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
\label{def:shannon-code}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]<\epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that we require the code to correct random errors of every size $t'<t$\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

@@

 \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]<\epsilon$.
\end{definition}
An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.  See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.  An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.  We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.  There is a set $\mathcal{C}'$ with $|\mathcal{C}'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We can now formalize the intuition above and show that a sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Let $s_{rec}$ denote the size of the circuit that computes $\rec$.  If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $\mathcal{C}$ with $|\mathcal{C}|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

%It is known (see \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein) that, 
For the Hamming metric, any Shannon code (as defined in Definition~\ref{def:shannon-code}) can be converted into an information-theoretic secure sketch~(as described in \cite[Section 8.2]{DBLP:journals/siamcomp/DodisORS08} and references therein).  The idea is to use the code offset construction, and convert worst-case errors to random errors by randomizing the order of the bits of $w$ first, via a randomly chosen  permutation $\pi$  (which  becomes part of the sketch and is applied to $w'$ during $\rec$). The formal statement is in the following Lemma.\bnote{I feel we should cite this.}
\begin{lemma}
\label{lem:shannon to sketch}
For an alphabet $Z$, let $\mathcal{C}$ over $Z^n$ be a $(t, \delta)$ Shannon code.  % with recovery procedure $\rec'$.
%  Let $W$ be a distribution with $\Hoo(W)\geq k$. 
%
% Define the following procedures
%\lnote{I think this description is buggy}
%\begin{center}
%\begin{tabular}{c|c}
%\begin{minipage}{3in}
%\textbf{\sketch}
%\begin{enumerate}
%\item Input $w\leftarrow W$.
%\item Sample $\pi$ from the space of all permutations from $\pi: [n]\rightarrow [n]$.
%\item Sample $c\leftarrow \mathcal{C}$.
%\item Apply $\pi$ bitwise to get $x_i = w_{\pi(i)}$.
%\item Output $p = x \oplus c, \pi$.
%\end{enumerate}
% \end{minipage} &
%\begin{minipage}{3in}
%\textbf{\rec}
%\begin{enumerate}
%\item Input $(w', p, \pi)$
%\item Apply $\pi^{-1}$ bitwise to get $x_i' = w_{\pi(i)}$.
%\item Compute $c' = p \oplus x'$.
%\item Compute $c = \rec'(c)$.
%\item Output $p\oplus c$.
%\\
%\end{enumerate}
%\end{minipage} 
%\end{tabular}
%\end{center}
Then there exists a $(Z^n, m, m-(n\log|Z|-\log |\mathcal{C}|), t)$ secure sketch with error $\delta$ for the Hamming metric over $Z^n$. 
%satisfies the following properties~(probability over the choice of $\pi$ in $\sketch$):
%\begin{itemize}
%\item Correctness: $\forall w, w'$ where $dis(w, w')\leq t$, $\Pr[\rec(w', \sketch(w))\neq w]<\epsilon$.
%\item Security: $\Hav(W |\sketch(W)) \geq \Hoo(W) - (n-\log |C|)$.
%\item Efficiency: $\sketch$ is efficient if sampling from $C$ is efficient and $\rec$ is efficient if $\rec'$ is efficient.
%\end{itemize}
\end{lemma}
%\begin{construction}
%Let $\delta >0$ be a parameter.
%Let $C$ be a $(t, \epsilon)$ Shannon code over $\{0,1\}^n$.  Choose a permutation $\pi:\mathcal{M}rightarrow \mathcal{M}$ that is $\beta$-almost independent $\ell = \delta n/\log(n)$-wise permutation.  Thefn for $\beta = 2^{-\ell}
%\end{construction}
Putting together \thref{thm:impSketchArbitraryW} and \lemref{lem:shannon to sketch} gives us the negative result for the Hamming metric: a HILL-entropy secure sketch (for the uniform distribution) implies an information-theoretic one with similar parameters:
\begin{corollary}
\label{cor:rec yields sketch}
Let $Z$ be an alphabet. Let $(\sketch', \rec')$ be an $(\epsilon,s_{sec})$-HILL-entropy $(Z^n, n\log |Z|, \tilde{m}, t)$-secure sketch with error $\delta$ for the Hamming metric over $Z^n$, with $\rec'$ of circuit size $s_{rec}$.
If $s_{sec}\geq t(s_{rec} + n\log |Z|)$, then there exists a   $(Z^n, n\log |Z|, \tilde{m}-2,t)$ (information-theoretic) secure sketch with error
$4(\epsilon+t\delta)$. 
%Let $(\mathcal{M}, d)$ be a metric space that is $(s_{neigh}, t)$-neighborhood samplable.  If no $(t, \epsilon)$-average error Shannon code over $\mathcal{M}$ exists of size $2^k$ then, $\forall (s_{rec}, t)$ recovery procedures $(\sketch, \rec)$ $H^{\hill}_{\epsilon, s}(X|\sketch(X))\not\geq k$ for $s=O(s_{rec}+s_{neigh})$.
\end{corollary}
\textbf{Notes:} In \corref{cor:rec yields sketch} we make no claim about the efficiency of the resulting  $(\sketch, \rec)$, because the proof of \thref{thm:impSketchArbitraryW} is not constructive.

@@

\begin{definition}~\cite[Definition 7]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{def:unp entropy}
For a distribution $(W, S)$, we say that $W$ has \emph{unpredictability entropy} at least $k$ conditioned on $S,$ denoted by $H^{\unp}_{\epsilon, s_{sec}} (W|S) \geq k$, if there exists a collection of distributions $X_s$ (giving rise to a joint distribution $(X, S)$) such that $\delta^{\mathcal{D}_{s_{sec}}}((W, S),(X, S))\leq \epsilon$, and for all circuits $\mathcal{I}$ of size $s_{sec}$,
\[
\Pr[\mathcal{I}(Z) = Y ] \leq 2^{-k}
.\]
\end{definition}
We will say a pair of procedures $(\sketch, \rec)$ is a \emph{unpredictability-entropy $(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon, s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch} with the security requirement replaced with $H^{\unp}_{\epsilon, s_{sec}}(W| \sketch(W))\geq \tilde{m}$.  
We consider this notion to be a natural notion for a computational sketch as it can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}):
\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
\label{lem:unp extraction} 
\bnote{We can't use the letter $C$ its taken for a distribution of codewords.}\bnote{We also $D$ as a distinguisher elsewhere.}
Let $W$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(W|S)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(W, U_d), S), U_m\times U_d\times S)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
\end{lemma}
Thus, if a sketch retained unpredictability entropy we could build a computational fuzzy extractor~(using the construction in \lemref{lem:fuzzy ext construction}).  
Unfortunately, the unpredictability entropy conditioned on the sketch must decrease as $t$ increases.  
%An adversaries ability to predict the output of the \rec algorithm increases with as $t$ grows.  %That is, $\forall Y$ such that $\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)) , (Y, \sketch(W))$ our ability to predict $Y$ increases as $|B_t(\cdot)|$ increases.  
The formal statement is below:
\bnote{Should we list the stronger statement in the appendix or keep this for clarity?}
\begin{theorem}
\label{thm:imp of unp entropy}
Let $W$ be a distribution over $Z^n$ and let $(\sketch, \rec)$ be an unpredictability-entropy \\$(Z^n, \Hoo(W), \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  If $s_{sec} \geq t(|\rec|+n\log |Z|)$, then $\tilde{m}\leq n\log |Z| - \log |B_t(\cdot)| + \log(1-\epsilon -t\delta)$.
\end{theorem}
This result has a weaker condition than \corref{cor:rec yields sketch} and yields a weaker conclusion.  The main difference with \thref{thm:impSketchArbitraryW} is that it is unknown if the indistinguishable distribution contains many points.  This means we cannot construct a good code out of the points of $Y$.  In \secref{sec:proof of imp unp entropy}, we prove a stronger theorem for larger class of metric spaces and for a relaxed notion of unpredictability entropy~(similar to the relaxed notion of HILL entropy in \defref{def:relaxed hill}).%Our bound is a result of the Hamming bound for the space.
